Predicting I/O-performance in HPC using Artificial Neural Networks

### 2016-06-29 Paper/paper.tex
access sizes

To study the distribution of measured file access times we display them as follows:
All measurements with equal access size have the same color, access sizes of file accesses are increasing in the graphs from left to right.
The resulting graphs can be seen in the Figures \ref{src/plot_SizeSorted_log_read_seq_sizes.png} to \ref{src/plot_SizeSorted_log_write_rnd.png}.

@@

\fig{width=.47\textwidth}{src/plot_SizeSorted_log_read_seq_sizes.png}{Measurements of sequential reading file accesses.}
\fig{width=.47\textwidth}{src/plot_SizeSorted_log_write_seq.png}{Measurements of sequential writing file accesses.}
\fig{width=.47\textwidth}{src/plot_SizeSorted_log_read_rnd.png}{Measurements of random reading file accesses.}
\fig{width=.47\textwidth}{src/plot_SizeSorted_log_write_rnd.png}{Measurements of random writing file accesses.}
For clarity the slowest and fastest 1\% of measurements are cut and only every 25th measurement is represented.\\
The correlation between access size and access time can be easily identified.
As described in chapter \ref{sec:path_for_pred} the split of measurements with equal access parameter values, that occurs in particular in the cases of sequential file accesses, can be explained with a processing in the storage system along different I/O-paths.
Worth mentioning is that the groups of access time for different access sizes are partially at the same range of magnitude.
This indicates as well that the splits are caused by varying I/O-paths as one I/O-path has a typical access time, which only changes slightly for different access sizes.\\
The phenomenon of these splits clarifies why despite of the strong correlation of access size to access time a linear model might produce sub-optimal predictions. It's difficult to predict which I/O-path will be used for a measurement as they differentiate for equal access parameter values.
In Figure \ref{src/plot_SizeSorted_log_read_rnd.png} the importance of knowledge about I/O-paths for the  access time prediction can be seen, for example file accesses of only 1\,B can be processed as slow as accesses with 16\,MiB if the longest I/O-path is used.\\
For writing file accesses the splits only occur occasionally and are less drastic; these measurements might be well represented with a linear model.

>>>>

To study the distribution of measured file access times we display them as follows:
All measurements with equal access size have the same color, access sizes of file accesses are increasing in the graphs from left to right.
The resulting graphs can be seen in the Figures \ref{src/plot_SizeSorted_log_read_seq2.png} to \ref{src/plot_SizeSorted_log_write_rnd.png}.

@@

\fig{width=.47\textwidth}{src/plot_SizeSorted_log_read_seq2.png}{Measurements of sequential reading file accesses.}
\fig{width=.47\textwidth}{src/plot_SizeSorted_log_write_seq.png}{Measurements of sequential writing file accesses.}
\fig{width=.47\textwidth}{src/plot_SizeSorted_log_read_rnd.png}{Measurements of random reading file accesses.}
\fig{width=.47\textwidth}{src/plot_SizeSorted_log_write_rnd.png}{Measurements of random writing file accesses.}
For clarity the slowest and fastest 1\% of measurements are cut and only every 25th measurement is represented.\\
The correlation between access size and access time can be easily identified.
As described in chapter \ref{sec:path_for_pred} the split of measurements with equal access parameter values, that occurs in particular in the cases of sequential file accesses, can be explained with a processing in the storage system along different I/O-paths.
Worth mentioning is that the groups of access time for different access sizes are partially at the same range of magnitude.
This indicates as well that the splits are caused by varying I/O-paths as one I/O-path has a typical access time, which only changes slightly for different access sizes.\\
The phenomenon of these splits clarifies why despite of the strong correlation of access size to access time a linear model might produce sub-optimal predictions. It's difficult to predict which I/O-path will be used for a measurement as they differentiate for equal access parameter values.
In Figure \ref{src/plot_SizeSorted_log_read_rnd.png} the importance of knowledge about I/O-paths for the  access time prediction can be seen, for example file accesses of only 1\,B can be processed as slow as accesses with 16\,MiB if the longest I/O-path is used.\\
For writing file accesses the splits only occur occasionally and are less drastic; these measurements might be well represented with a linear model.
